\documentclass[oneside,english]{amsbook}
\usepackage{lmodern}
\renewcommand{\sfdefault}{lmss}
\renewcommand{\ttdefault}{lmtt}
\renewcommand{\familydefault}{\rmdefault}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{esint}
\usepackage[all]{xy}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{section}{chapter}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
  \theoremstyle{definition}
  \newtheorem{defn}[thm]{\protect\definitionname}
  \theoremstyle{remark}
  \newtheorem*{rem*}{\protect\remarkname}
  \theoremstyle{definition}
  \newtheorem*{example*}{\protect\examplename}
 \theoremstyle{definition}
 \newtheorem*{defn*}{\protect\definitionname}
  \theoremstyle{plain}
  \newtheorem*{cor*}{\protect\corollaryname}

\makeatother

\usepackage{babel}
  \providecommand{\corollaryname}{Corollary}
  \providecommand{\definitionname}{Definition}
  \providecommand{\examplename}{Example}
  \providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}

\begin{document}

\title{Hitchin Systems Seminar}

\maketitle
\tableofcontents{}


\chapter{Introduction}

This course studies the Hitchin system from different perspectives and in various settings.

Hitchin studied a limiting form of the self-dual equations of Yang-Mills theory in four dimensions,
imposing invariance under two of the dimensions.  The resulting equations were found to be
conformally invariant with respect to the remaining two directions, so had a natural formulation
as equations on a Riemann surface.  The Hitchin moduli space, or moduli space of Higgs bundles,
will be defined as the space of solutions modulo gauge transformations.

Several basic properties of the space of solutions emerged.  First, the equations could be
interpreted formally as hyperkahler moment map equations for the compact gauge Group action
on the infinite-dimensional space of connections.  Since we quotient solutions by gauge
transformations, this means we have an interpretation of the Hithchin moduli space as a hyperkahler
quotient.  Thus it should inherit a hyperkaher structure.  Of the three independent complex structures,
the one most amenable to algebraic geometry is the one inherited from the complex
structue on the Riemann surface, $C$.  In that setting, the Hitchin moduli space has an
interpretation as stable Higgs pairs, i.e. pairs $(V,\varphi)$, where $V$ is a rank-$n$ holomorphic
vector bundle over $C$, and $\varphi\in \Gamma(End(V)\otimes K_C)$ is a holomorphic $n\times n$
matrix-valued one-form.  Stability requires that all $\varphi$-invariant sub-bundles have lesser slope
than $V$.  Finally, solutions are taken modulo holomorphic isomorphism of vector bundles.

Another structure which emerges is that of an algebraically completely integrable system.
Recall first that a complete integrable system on a symplectic manifold (``phase space'') is a
maximal set of Poisson-commuting proper functions (``Hamiltonians").  Specifying the values
of these conserved quantities gives a common level set which is a Lagrangian torus.
This gives another definition:  a fibration by Lagrangian tori to a base manifold where the
Hamiltonians take their values.  The fiber map for the Hitchin space is defined by all the
invariant polynomials $Tr\varphi^k$.

Local study....




\chapter{Overview and Definitions}


\chapter{Symplectic Quotients in Finite and Infinite Dimensions}


\chapter{Hyperkahler Quotients and Integrable Systems}


\chapter{Stability and the Narasimhan-Seshadri Theorem}


\chapter{Teichmueller Theory}


%% Matthew's talk #1 
\chapter{Construction of the Hitchin Moduli Space}


This talk closely follows \cite{H1}. In this chapter, it is shown
that the Hitchin moduli space $\mathcal{M}_{H}$ is a smooth manifold
of dimension $12(g-1)$. We also prove that $\mathcal{M}_{H}$ is
equipped with a complete hyperkahler metric. 


\section{Definitions}

Let $M$ be a Riemannian surface, $P\rightarrow M$ a principal $G=SO\left(3\right)$-bundle,
$V$ the associated rank 2 vector bundle, and $\mathcal{G}$ the group
of gauge transformations ($\mathcal{G}=Map\left(M,G\right)$). Recall
that for a connection $A$ on $P$ and $\Phi\in\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)$,
the self-dual equations are 
\begin{align*}
\tag{\ensuremath{\star}}F_{A}+\left[\Phi,\Phi^{*}\right] & =0,\\
\overline{\partial_{A}}\Phi & =0
\end{align*}


For a connection $A$, $u\in\mathcal{G}$ acts by 
\[
u\left(A\right)=uAu^{-1}-\left(du\right)u^{-1}
\]
(where the covariant derivative is $\nabla_{A}=d+A\wedge$, i.e.,
\[
\nabla_{u\left(A\right)}s=u\nabla_{A}\left(u^{-1}s\right)
\]
for a section $s$ of $V$.

For $\Phi\in\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)$, $u$
acts by 
\[
u\left(\Phi\right)=u\Phi u^{-1},
\]
where we regard $adP\otimes\mathbb{C}$ as the bundle of trace-zero
endomorphisms of $V$.
\begin{defn}
The Hitchin moduli space is 
\[
\mathcal{M}_{H}:=\left\{ \mbox{solutions to (}\star\mbox{)}\right\} /\mathcal{G}.
\]
\end{defn}
\begin{description}
\item [{Goal}] To learn about the geometry and topology of $\mathcal{M}_{H}$.
\end{description}

\section{Summary of results}

Let $V$ be a rank 2, odd degree vector bundle over a Riemannian surface
$M$. Then, 
\begin{itemize}
\item $\mathcal{M}_{H}$ is a smooth manifold of dimension $12\left(g-1\right)$.
\item $\mathcal{M}_{H}$ has a natural metric.
\item $\mathcal{M}_{H}$'s metric is complete and hyperkahler (in fact,
$\mathcal{M}_{H}$ is a hyperkahler quotient).\end{itemize}
\begin{rem*}
$V$ has odd degree $\implies$ there are no reducible solutions to
$\left(\star\right)$ $\implies$ $\mathcal{G}$ acts freely on $\left(\star\right)$.
\end{rem*}

\section{$\mathcal{M}_{H}$ is a dimension $12\left(g-1\right)$ smooth manifold}

First, to get the expected dimension, we compute the dimension of
the tangent space to $\mathcal{M}_{H}$ at a regular point (i.e.,
one with trivial isotropy group). 


\subsection{Idea of Proof}
\begin{itemize}
\item Linearize $(\star)$ to determine the expected dimension.
\item Let $\left(A\times\Omega\right)_{0}$ denote ``regular points,''
i.e., ones which are only fixed by the identity in $\mathcal{G}$
(those with trivial isotropy group). Then, exhibit $\mathcal{M}_{H}$
is a smooth submanifold of $\left(\mathcal{A}\times\Omega\right)_{0}/\mathcal{G}$
using the regular value theorem.
\end{itemize}

\subsection{Linearization of $(\star)$}

Let $\left(\dot{A},\dot{\Phi}\right)\in\Omega_{M}^{1}\left(adP\right)\oplus\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)$.
To get the linearization of $(\star$), fix a base point $\left(A,\Phi\right)$
and look at 
\[
\left.\frac{d}{dt}\right|_{t=0}\left(\star\right)\left(A+t\dot{A},\Phi+t\dot{\Phi}\right).
\]
Recalling that $F_{A}=dA+A\wedge A$, the first equation becomes 
\[
d_{A}\dot{A}+\left[\dot{\Phi},\Phi^{*}\right]+\left[\Phi,\dot{\Phi}^{*}\right]=0,
\]
and the second is 
\[
\overline{\partial_{A}}\dot{\Phi}+\dot{A}^{0,1}\wedge\Phi=0.
\]


$\left(\dot{A},\dot{\Phi}\right)$ arises from an infinitesimal gauge
transformation $\dot{\psi}\in\Omega_{M}^{0}\left(adP\right)$ if 
\begin{align*}
\dot{A} & =d_{A}\dot{\psi}, & \dot{\Phi} & =\left[\Phi,\dot{\psi}\right].
\end{align*}
Let 
\begin{eqnarray*}
d_{1}:\Omega_{M}^{0}\left(adP\right) & \longrightarrow & \Omega_{M}^{1}\left(adP\right)\oplus\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)\\
\dot{\psi} & \mapsto & \left(d_{A}\dot{\psi},\left[\Phi,\dot{\psi}\right]\right)
\end{eqnarray*}
and 
\begin{eqnarray*}
d_{2}:\Omega_{M}^{1}\left(adP\right)\oplus\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right) & \longrightarrow & \Omega_{M}^{2}\left(adP\right)\oplus\Omega_{M}^{2}\left(adP\otimes\mathbb{C}\right)\\
\left(\dot{A},\dot{\Phi}\right) & \mapsto & \left(d_{A}\dot{A}+\left[\dot{\Phi},\Phi^{*}\right]+\left[\Phi,\dot{\Phi}^{*}\right],\overline{\partial_{A}}\dot{\Phi}+\dot{A}^{0,1}\wedge\Phi\right).
\end{eqnarray*}
Then, $d_{1},d_{2}$ define an \emph{elliptic complex} with index
$3\left(2-2g\right)-6\left(g-1\right)=12\left(1-g\right)$. The Atiyah-Singer
index theorem then says that 
\[
\dim H^{0}-\dim H^{1}+\dim H^{2}=12\left(1-g\right).
\]



\subsection{Elliptic Complexes}

Now, a short digression into elliptic complexes. Let $X$ be a manifold,
$\pi:T^{*}X\rightarrow X$ be projection onto the base, and $\left\{ E_{k}\rightarrow X\right\} $
a collection of vector bundles over $X$. 
\begin{defn}
A chain complex 
\[
\xymatrix{\cdots\ar[r] & \Gamma\left(E_{k-1}\right)\ar[r]^{P_{k-1}} & \Gamma\left(E_{k}\right)\ar[r]^{P_{k}} & \Gamma\left(E_{k+1}\right)\ar[r] & \cdots}
\]
is \textbf{elliptic} if the corresponding sequence of symbols 
\[
\xymatrix{\cdots\ar[r] & \pi^{*}E_{k-1}\ar[r]^{\sigma\left(P_{k-1}\right)} & \pi^{*}E_{k}\ar[r]^{\sigma\left(P_{k}\right)} & \pi^{*}E_{k+1}\ar[r] & \cdots}
\]
is exact.\end{defn}
\begin{example*}
Let $P:E_{1}\rightarrow E_{2}$ be a differential operator. Then,
the complex 
\[
\xymatrix{0\ar[r] & \Gamma\left(E_{1}\right)\ar[r]^{P} & \Gamma\left(E_{2}\right)\ar[r] & 0}
\]
is elliptic means that 
\[
\xymatrix{0\ar[r] & \pi^{*}E_{1}\ar[r]^{\sigma\left(P\right)} & \pi^{*}E_{2}\ar[r] & 0}
\]
is exact, i.e., that $\sigma\left(P\right):\pi^{*}E_{1}\rightarrow\pi^{*}E_{2}$
is an isomorphism. Recall that this is the ``usual'' definition
of elliptic differential operator. 
\end{example*}
Now, return to our elliptic complex. 

\[
\xymatrix{\Omega_{M}^{0}\left(adP\right)\ar[r]^-{d_{1}} & \Omega_{M}^{1}\left(adP\right)\oplus\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)\ar[r]^-{d_{2}} & \Omega_{M}^{2}\left(adP\right)\oplus\Omega_{M}^{2}\left(adP\otimes\mathbb{C}\right)\\
\dot{\psi}\ar@{|->}[r] & \left(d_{A}\dot{\psi},\left[\Phi,\dot{\psi}\right]\right)\\
 & \left(\dot{A},\dot{\Phi}\right)\ar@{|->}[r] & \left(d_{A}\dot{A}+\left[\dot{\Phi},\Phi^{*}\right]+\left[\Phi,\dot{\Phi}^{*}\right],\overline{\partial_{A}}\dot{\Phi}+\dot{A}^{0,1}\wedge\Phi\right)
}
\] 

By construction, we're interested in $H^{1}$ of this complex: $H^{0}=\ker d_{1}$
is the covariantly constant $\dot{\psi}$ which commute with $\Phi$.
These correspond to reducible solutions to $(\star$). So, if $H^{0}\neq0$,
then $\left(A,\Phi\right)$ is reducible. In fact, by considering
$d_{2}^{*}$, we can show that $H^{2}=0$ as well \cite{H1}. Hence,
\[
-\dim H^{1}=12\left(1-g\right),
\]
i.e., for a regular point $\left(A,\Phi\right)$, 
\[
\boxed{\dim T_{\left(A,\Phi\right)}\mathcal{M}_{H}=12\left(g-1\right)}.
\]



\subsection{$\mathcal{M}_{H}$ is a smooth manifold}

This is a sketch, for complete details see \cite{H1}. 
\begin{defn}
$\left(A,\Phi\right)$ is a \textbf{regular point} if the isotropy
group of $\left(A,\Phi\right)$ is the identity (i.e., there are no
nontrivial gauge transformations fixing this point).
\end{defn}
Recall that infinitesimally, these are the points where there are
no nonzero solutions to $d_{1}\dot{\psi}=0$. 

Let $\left(\mathcal{A}\times\Omega\right)_{0}$ denote the open set
of regular points in $\mathcal{A}\times\Omega$, and 
\[
B:=\left(\mathcal{A}\times\Omega\right)_{0}/\mathcal{G}.
\]
By construction, $B$ is a Banach manifold with the quotient topology.
We have the map 
\[
d_{1}^{*}:\Omega_{M}^{1}\left(adP\right)\oplus\Omega_{M}^{1,0}\left(adP\otimes\mathbb{C}\right)\longrightarrow\Omega_{M}^{0}\left(adP\right).
\]
Define a \emph{slice} of $\mathcal{M}_{H}$ to be $\ker d_{1}^{*}$,
at some fixed $\left(A_{0},\Phi_{0}\right)$---then, the slices provide
coordinate patchs for $B$. Set 
\begin{eqnarray*}
f:\ker d_{1}^{*} & \longrightarrow & \Omega_{M}^{2}\left(adP\right)\oplus\Omega_{M}^{2}\left(adP\otimes\mathbb{C}\right)\\
\left(A,\Phi\right) & \mapsto & \left(F_{A}+\left[\Phi,\Phi^{*}\right],\overline{\partial_{A}}\Phi\right);
\end{eqnarray*}
then, $f^{-1}\left(0,0\right)$ is a smooth submanifold of $\ker d_{1}^{*}$
with dimension $12(g-1)$. 

Since $\ker d_{1}^{*}$ form coordinate patches for $B$, the remainder
of the proof is just arguing that the $\ker d_{1}^{*}$ patch together
to form a smooth manifold. 


\section{The tangent space}

Thanks to our results in the previous section, we have an explicit
description of the tangent space to $\mathcal{M}_{H}$: 
\[
T_{\left(A,\Phi\right)}\mathcal{M}_{H}=\left\{ \left(\dot{A},\dot{\Phi}\right)\left|\begin{matrix}d_{A}\dot{A}+\left[\dot{\Phi},\Phi^{*}\right]+\left[\Phi,\dot{\Phi}^{*}\right]=0,\\
\overline{\partial_{A}}\dot{\Phi}+\dot{A}^{0,1}\wedge\Phi=0,\\
d_{A}^{*}\dot{A}+Re\left[\Phi^{*},\dot{\Phi}\right]=0.
\end{matrix}\right.\right\} 
\]
The third equation appears because $d_{1}^{*}\left(\dot{A},\dot{\Phi}\right)=d_{A}^{*}\dot{A}+Re\left[\Phi^{*},\dot{\Phi}\right]$. 


\section{$\mathcal{M}_{H}$ has a complete hyperkahler metric}

Recall from Sean's talk that the metric on $\mathcal{A}\times\Omega$
given by 
\[
g\left((\psi,\phi),\left(\psi,\phi\right)\right)=2i\int_{M}Tr\left(\psi^{*}\psi+\phi\phi^{*}\right)
\]
induces a metric on $T_{p}\mathcal{M}_{H}$. We want to show that
this is a complete metric on $T_{\left(A,\Phi\right)}\mathcal{M}_{H}$.
As a reminder:
\begin{defn*}
A metric on $M$ is \textbf{complete} if every Cauchy sequence of
points on $M$ has a limit which is also in $M$.
\end{defn*}

\subsection{Idea of Proof}

By contradiction: Suppose we have a sequence of points in $\mathcal{M}_{H}$
defined by a geodesic $\gamma$ converging to a point not in $\mathcal{M}_{H}$.
Because $g$ is $\mathcal{G}$-invariant, we can look at $\tilde{\mathcal{M}_{H}}\subset\mathcal{A}\times\Omega$.
Lift $\gamma$ to a horizontal $\tilde{\gamma}$ in $\tilde{\mathcal{M}}_{H}$.
$\tilde{\gamma}$ still defines a Cauchy sequence in $\tilde{\mathcal{M}}_{H}$,
so we have 
\[
||A_{n}-\overline{A}||_{L^{2}}^{2}+||\Phi_{n}-\overline{\Phi}||_{L^{2}}^{2}\leq C
\]
 for some $C$ as $\left(A_{n},\Phi_{n}\right)\rightarrow\left(\overline{A},\overline{\Phi}\right)$
(where $\left(\overline{A},\overline{\Phi}\right)$ is the limiting
point not in $\mathcal{M}_{H}$). 

Now, we apply Uhlenbeck's compactification theorem to show that there's
a gauge transformation taking $\left(\overline{A},\overline{\Phi}\right)$
to a solution of $(\star)$:
\begin{thm}
[Uhlenbeck] There are constants $\epsilon_{1}$, $M>0$ such that
any connection $A$ on the trivial bundle over $\overline{B}^{4}$
with $||F_{A}||_{L^{2}}<\epsilon_{1}$ is gauge equivalent to a connection
$\tilde{A}$ over $B^{4}$ with 
\begin{enumerate}
\item $d^{*}\tilde{A}=0$,
\item $\lim_{\left|x\right|\rightarrow1}\tilde{A}_{r}=0$, and 
\item $||\tilde{A}||_{L_{1}^{2}}\leq M||F_{\tilde{A}}||_{L^{2}}$. 
\end{enumerate}
Moreover for suitable constants $\epsilon_{1}$, $M$, $\tilde{A}$
is uniquely determined by these properties, up to $\tilde{A}\mapsto u_{0}\tilde{A}u_{0}^{-1}$
for a constant $u_{0}$ in $U\left(n\right)$.
\end{thm}
In particular, we can use the following corrollary:
\begin{cor*}
For any sequence of ASD connections $A_{\alpha}$ over $\overline{B}^{4}$
with $||F\left(A_{\alpha}\right)||_{L^{2}}\leq\epsilon$, there is
a subsequence $\alpha'$ and gauge equivalent connections $\tilde{A}_{\alpha'}$
which converge in $C^{\infty}$ on the open ball. 
\end{cor*}
Therefore, there's a gauge transformation taking $\left(\overline{A},\overline{\Phi}\right)$
to a solution of $(\star)$. This is a contradiction, so $\mathcal{M}_{H}$
is complete. 


\subsection{Hyperkahler structure}

Recall from Sean's talk that there's a symplectic form on $\mathcal{M}_{H}$
given by 
\[
\omega\left((\psi_{1},\phi_{1}),\left(\psi_{2},\phi_{2}\right)\right)=\int_{M}Tr\left(\phi_{2}\psi_{1}-\phi_{1}\psi_{2}\right).
\]
This defines a complex moment map from the action of $\mathcal{G}$:
\[
\mu\left(A,\Phi\right)=\overline{\partial}_{A}\Phi.
\]
We can write $\mu=\mu_{2}+i\mu_{3}$ and $\omega=\omega_{2}+i\omega_{3}$
to get two symplectic structures out of this. The third (or first?)
symplectic structure is just the Kahler form associated to the metric
\[
g=2i\int_{M}Tr\left(\psi^{*}\psi+\phi\phi^{*}\right),
\]
and has moment map 
\[
\mu_{1}\left(A,\Phi\right)=F_{A}+\left[\Phi,\Phi^{*}\right].
\]
This exhibits $\mathcal{M}_{H}$ as a hyperkahler quotient of $\mathcal{A}\times\Omega$:
\[
\mathcal{M}_{H}=\bigcap_{i=1}^{3}\mu_{i}^{-1}\left(0\right)/\mathcal{G}.
\]



\section{Summary of topological results}

Here, we state some topological results. For proofs, see section 7
of \cite{H1}.

$\mathcal{M}_{H}$ is...
\begin{itemize}
\item non-compact
\item connected and simply connected
\item the Betti numbers $b_{i}$ vanish for $i>6g-6.$
\end{itemize}


\chapter{Integrable Systems and Spectral Curves}


\chapter{Meromorphic Connections and Stokes Data}


\chapter{The Langlands Program and Relations to Geometric Langlands}


\chapter{Spectral Curves and Irregular Singularities}


\chapter{The Stokes Groupoid}


\chapter{Cluster Varieties}


\chapter{The Hitchin System and Teichmueller Theory II}


\chapter{Geometric Langlands and Mirror Symmetry}

% Matthew Talk 2
\chapter{Hitchin Systems and Supersymmetric Field Theories}

\section{Introduction and definitions}

In previous talks, we've explored many properties of the Hitchin system
and its geometry, as well as several applications. The core idea of
this talk is that, given a certain supersymmetric field theory, we
can obtain the Hitchin system as a moduli space associated to this
theory via a standard procedure in quantum field theories. Gaiotto,
Moore, and Neitzke \cite{GMN} use this approach to construct a canonical
coordinate system on the Hitchin moduli space. The goal of this talk
is to explain some of the language of supersymmetric quantum field
theories, and describe how we can obtain $\mathcal{M}_{H}$ from a
particular class of such theories. 


\subsection{Supersymmetry}

Consider $\mathbb{R}^{n}$. The \textbf{Poincare group} is the group
of translations and rotations of this space: $G=ISO(n)\cong\mathbb{R}^{n}\rtimes SO(n)$.
(In Minkowski signature, say for $\mathbb{R}^{n,1}$, we might write
$ISO(n,1)$ instead). Recall that there's a spin group defined as
a double cover of $SO(n)$: 
\[
\xymatrix{1\ar[r] & \mathbb{Z}_{2}\ar[r] & Spin(n)\ar[r] & SO(n)\ar[r] & 1.}
\]
When we have such a double cover, we get an extension of the group
$G$ to the supergroup $\tilde{G}$. This gives an extension of the
Poincare algebra $\mathfrak{g}$ to the \textbf{super Poincare algebra}
$\tilde{\mathfrak{g}}$ coming from the double-cover of $SO(n)$.
$\tilde{\mathfrak{g}}$ is called the \textbf{supersymmetry algebra}.
Such $\tilde{g}$ are labelled by a choice of a representation of
$Spin(n)$. For irreducible representations of $Spin(n)$, there are
two possible cases:
\begin{itemize}
\item There is either a unique irreducible spinor representation $S$, and
any spinor representation has the form $S^{\oplus N}$ for some $N$,
or
\item There are two distinct irreducible real spinor representations $S_{+},S_{-}$,
and any spinor representation has the form $S_{+}^{\oplus N_{1}}\oplus S_{-}^{\oplus N_{2}}$
for some $N_{1},N_{2}$. (This occurs in dimensions $n\equiv2,6\mod8$). 
\end{itemize}
Thus, when someone says $N=n$ or $N=\left(n_{1},n_{2}\right)$ supersymmetry,
they are specifying which extension of the Poincare algebra they're
referring to.

The supersymmetry Lie algebra $\tilde{\mathfrak{g}}$ splits into
an even and odd part: 
\[
\tilde{\mathfrak{g}}=\mathfrak{g}^{0}\oplus\mathfrak{g}^{1},
\]
and is equipped with a skew-symmetric bracket $\left[\cdot,\cdot\right]:\tilde{\mathfrak{g}}\rightarrow\tilde{\mathfrak{g}}$
which satisfies the Jacobi identity. Note that $\left[\mathfrak{g}^{1},\mathfrak{g}^{1}\right]\subset\mathfrak{g}^{0}$,
$\mathfrak{g}^{0}=\mathfrak{g}$ (the Poincare algebra), and $\mathfrak{g}^{1}$
is just a linear representation of $\mathfrak{g}^{0}$. 
\begin{example*}
For $N=2$ SUSY and $G=ISO(3,1)$, we'll be interested in a $\tilde{G}$
whose Lie algebra has even part 
\[
\mathfrak{g}^{0}=\mbox{\ensuremath{\mathfrak{iso}}}(3,1)\oplus\mathbb{C}.
\]
The abelian $\mathbb{C}$ factor is central in $\tilde{\mathfrak{g}}$,
and has a canonical generator $Z$. 
\end{example*}

\subsection{BPS States}

Let $\mathcal{H}$ denote the Hilbert space of states of our quantum
system on $\mathbb{R}^{3,1}$. We want to think of a state as being
labeled by a representation of $\tilde{G}$---the representation encodes
the data of the particle. For example, the vacuum state (``empty
space'') in $\mathcal{H}$ corresponds to the trivial representation
of $\tilde{G}$. The next simplest kind of state is one where space
is empty except for a single particle propogating with some definite
momentum $p\in T^{*}\mathbb{R}^{3,1}$. Call the subspace of the Hilbert
space consisting of single-particle states $\mathcal{H}^{1}$. Here,
there's some structure:
\begin{itemize}
\item $\mathcal{H}^{1}$ splits into components $\mathcal{H}_{M}^{1}$,
labeled by $M\in\mathbb{R}_{\geq0}$. $M^{2}$ is the eigenvalue of
a quadratic Casimir operator in $ISO(3,1)$. Physically, it's the
mass of the particle. 
\item For $N=2$ SUSY as in our prior example, we also have a central generator
$Z\in\mathbb{C}$. Together, these give a decomposition 
\[
\mathcal{H}^{1}=\bigoplus_{M,Z}\mathcal{H}_{M,Z}^{1}.
\]

\end{itemize}
Fix some momentum $p_{rest}\in\left(\mathbb{R}^{3,1}\right)^{*}$
with $||p_{rest}||^{2}=M^{2}$, and consider the subspace $\mathcal{H}_{M,Z}^{1,rest}$
on which the subgroup of translations along $\mathbb{R}^{3,1}$ acts
by $p_{rest}$. This is a representation of a subgroup $\tilde{G}_{rest}\subset\tilde{G}$
with 
\[
\tilde{G}_{rest}=SO\left(3\right)\ltimes\tilde{T},
\]
where the ``super translation group'' $\tilde{T}$ is generated
by the ordinary translations $T=\mathbb{R}^{3,1}$ plus the central
character $Z$ and the ``odd translations'' $\mathfrak{g}^{1}$.
The odd translations act by a Clifford algebra (on an 8-dimensional
vector space). We can then count the number of unitary irreducible
representations of this Clifford algebra:
\begin{itemize}
\item If $M<\left|Z\right|$, then there are \emph{no} unitary representations
of the Clifford algebra.
\item If $M=\left|Z\right|$, the Clifford algebra is degenerate, and its
unique unitary irrep $S$ has dimension $2^{4/2}=4$. 
\item If $M>\left|Z\right|$, the Clifford algebra is nondegenerate, and
its unique unitary irrep $S$ has dimension $2^{8/2}=16$. 
\end{itemize}
States that satisfy $M=\left|Z\right|$ are called \textbf{BPS} (Bogomol'nyi,
Prasad, Sommerfield) \textbf{states}, and as one might expect, they
satisfy a set of differential equations depending on the field theory.
The BPS states are those in which half of the supersymmetry generators
are unbroken. 


\subsection{Moduli of Vacua}

The ``moduli space'' associated to a QFT typically refers to the
moduli space of vacua. By \textbf{vacua}, we mean the quantum state
with the lowest possible energy.
\begin{description}
\item [{Question}] In what sense is the space of vacua a moduli space?
\end{description}
For scalar fields, these are labelled by the \textbf{vacuum expectation
value} (VEV). The VEV of an operator is (as the name suggests) the
expectation value of the operator in the vacuum (the quantum state
with the lowest possible energy). We can label a vacuum state by its
VEV, and this gives a moduli space of vacua. 

For $N=2$ SUSY, the superalgebra has two representations with scalars:
\textbf{vectormultiplets} (one complex scalar), and \textbf{hypermultiplets}
(two complex scalars). This gives a local splitting of the moduli
of vacua $\mathcal{M}$ as 
\[
\mathcal{M}=\mathcal{M}_{C}\oplus\mathcal{M}_{H},
\]
where $\mathcal{M}_{C}$ is the ``Coulomb branch'' (vectormultiplets),
and $\mathcal{M}_{H}$ is the ``Higgs branch'' (hypermultiplets). 


\section{Compactification and Dimensional Reduction}

Compactification of a field theory is a process where, instead of
considering a general space $X$, we consider $X=M\times C$ where
$C$ is some compact space. Dimensional reduction is the limit of
the compactified theory where the volume of the compact space is shrunk
to zero, which produces an effective theory on the remaining dimensions. 
\begin{example*}
[Toy Example] Consider a field theory on $X=\mathbb{R}^{n}\times S_{R}^{1}$
($S_{R}^{1}$ is the circle of radius $R$). Let $\theta$ be a coordinate
on $S_{R}^{1}$, and $x^{i}$ coordinates on $\mathbb{R}^{n}$. At
a fixed $x$ coordinate, the fields along the $S_{R}^{1}$ look like
\[
\phi|_{x}=\sum_{n}A_{n}\cos\left(\frac{2\pi n}{R}\theta\right)+B_{n}\sin\left(\frac{2\pi n}{R}\theta\right),
\]
where the coefficients $A_{n}$ and $B_{n}$ are determined by the
boundary conditions on $\phi$. As $R\rightarrow0$, the eigenvalues
$\lambda_{n}=\frac{2\pi n}{R}$ approach $\infty$, except for $n=0$.
Note that in quantum mechanics, $\hbar\lambda_{n}$ is the \emph{momentum}
of eigenstate $n$, so as $R\rightarrow\infty$, all mometums except
the trivial one also $\rightarrow\infty$. We should interpert $R\rightarrow0$
as meaning that, for finite energy (and hence, finite momentum), the
only eigenstate left is the trivial one. 

If $\phi|_{x}$ is constant, it means that the field $\phi$ does
not depend on $\theta$---the dimensional reduction of the theory
on $S_{R}^{1}$ consists of the fields of the $\mathbb{R}^{n}\times S_{R}^{1}$
theory which do not depend on $\theta$.
\end{example*}
So, we have two equivalent perspectives on dimensional reduction to
$M$ of a theory on a space $M\times C$:
\begin{itemize}
\item It's the limit of the theory on $M\times C$ where the volume of $C$
contracts to zero, or
\item It's the theory on $M\times C$ where all fields are taken to be independent
of coordinates on $C$.
\end{itemize}

\begin{example*}
[Yang-Mills] We actually already encountered dimensional reduction
in one of the first lectures of the course. Consider classical Yang-Mills
theory.

Yang-Mills theory is a field theory defined for principal $G$-bundles
$P\rightarrow X$, where $X$ is a 4-dimensional Riemannian manifold. 
\begin{description}
\item [{Fields}] Connections $A$ on $P$.
\item [{Lagrangian}] 
\[
L\left(A\right)=\left|F_{A}\right|^{2}d\mu
\]

\end{description}
Recall that from the Lagrangian, we obtain the action functional by
\[
S\left(A\right)=\int_{X}L\left(A\right)=\int_{X}\left|F_{A}\right|^{2}d\mu.
\]
The equations of motion for Yang-Mills theory are 
\[
d_{A}^{*}F_{A}=0,
\]
and the instantons are the (anti) self-dual connections: 
\[
F_{A}=\pm*F_{A}.
\]
(Here, $*:\Omega_{X}^{2}\cong\Omega_{X}^{2}$ is the Hodge star operator).

In local coordinates we can write $d_{A}=d+A$, where 
\[
A=A_{1}dx_{1}+A_{2}dx_{2}+A_{3}dx_{3}+A_{4}dx_{4}.
\]
Define 
\[
F_{ij}:=\left[\nabla_{i},\nabla_{j}\right]=\frac{\partial}{\partial x_{i}}A_{j}-\frac{\partial}{\partial x_{j}}A_{i}+\left[A_{i},A_{j}\right].
\]
Look at the self-dual connections. Then, the instanton equation $F_{A}^{-}=0$
becomes 
\begin{eqnarray*}
F_{12} & = & F_{34},\\
F_{13} & = & -F_{24},\\
F_{14} & = & F_{23}.
\end{eqnarray*}


Let's restrict attention to $X=C\times\mathbb{R}^{2}$, where $C$
is a Riemann surface. Suppose that we compactify and perform dimensional
reduction in $\mathbb{R}^{2}$ coordinates: restrict to $A_{j}$ which
are invariant under translation in $x_{3}$, $x_{4}$. Then, $A_{1}dx_{1}+A_{2}dx_{2}$
defines a connection on $C$. Relabel $A_{3}=\phi_{1}$ and $A_{4}=\phi_{2}$,
and define $\varphi=\phi_{1}-i\phi_{2}$; then the self-dual equations
become 
\begin{eqnarray*}
F_{A}-\frac{1}{2}i\left[\varphi,\varphi^{*}\right] & = & 0,\\
\left[\nabla_{1}+i\nabla_{2},\varphi\right] & = & 0.
\end{eqnarray*}
If we think of $\varphi$ as defining a local section of $\Omega^{0}\left(C;ad(P)\otimes\mathbb{C}\right)$,
and set $\Phi=\frac{1}{2}\varphi dz\in\Omega^{1,0}\left(ad\left(P\right)\otimes\mathbb{C}\right)$
and $\Phi^{*}=\frac{1}{2}\varphi^{*}d\overline{z}\in\Omega^{0,1}\left(ad(P)\otimes\mathbb{C}\right)$,
then the equations become 
\begin{eqnarray*}
F_{A}+\left[\Phi,\Phi^{*}\right] & = & 0,\\
\overline{\partial_{A}}\Phi & = & 0,
\end{eqnarray*}
the usual Hitchin equations.
\end{example*}

\section{5D Super Yang-Mills Theory}

Now, let's repeat the previous example, but including some supersymmetry.
5D Super Yang-Mills theory admits a conventional Lagrangian description:
Let $P$ be a principal $G$-bundle over $X$ (a 5-dimensional space).
The theory has: 
\begin{description}
\item [{Fields}] Connections $A$ on $P$, sections $\phi^{i}$ of $Ad\left(P\right)$
($i=1,\ldots,5$), and fermions.
\item [{Lagrangian}] 
\[
L=\frac{R}{8\pi^{2}}Tr\left[\frac{1}{R^{2}}F_{A}\wedge*F_{A}+\sum_{i=1}^{5}d_{A}\phi^{i}\wedge*d_{A}\phi^{i}+\mbox{fermions}\right].
\]
\end{description}
\begin{rem*}
~
\begin{enumerate}
\item 5D SYM is well-defined as an effective field theory, below a certain
energy scale. It is not obviously well-defined at arbitrarily high
energies. 
\item There's this unusual $R$ factor appearing here that you should be
suspicious of. We'll explain where this comes from at the end of the
talk.
\end{enumerate}
\end{rem*}

\subsection*{Compactification on $C$}

Let's take $X=\mathbb{R}^{2,1}\times C$, where $C$ is a Riemann
surface. Analogous to the classical case, when we compactify 5D SYM
on $C$, we combine $\phi^{4}$ and $\phi^{5}$ into a complex-valued
1-form on $C$: 
\[
\varphi=\left(\phi^{4}+i\phi^{5}\right)dz.
\]
Again, to do dimensional reduction, we require translation invariance---this
time along $\mathbb{R}^{2,1}$. 
\begin{description}
\item [{Question}] What are the classical field configurations in the compactified
theory which preserve the supersymmetry? (Recall that these are the
BPS states!)
\end{description}
Assuming $\phi^{1},\phi^{2},\phi^{3}=0$, the equations satisfied
by the remaining fields are 
\[
\tag{\ensuremath{\star}}\begin{cases}
 & F_{A}+R^{2}\left[\varphi,\varphi^{*}\right]=0,\\
 & \overline{\partial_{A}}\varphi=0,
\end{cases}
\]
which we recognize as (almost) Hitchin's equations. In other words,
the moduli space of vacua of $SYM[C]$ in the low energy limit is
\[
M_{C}\left[G\right]=\left\{ \mbox{solutions to }(\star)\right\} /\left\{ \mbox{gauge transformations}\right\} =\mathcal{M}_{H}.
\]

\begin{rem*}
We took $\phi^{1}=\phi^{2}=\phi^{3}=0$ above. If we don't, SUSY also
imposes equations on $\phi^{1},\phi^{2},\phi^{3}$: 
\begin{align*}
d_{A}\phi^{i} & =0, & \left[\varphi,\phi^{i}\right] & =0, & \left[\phi^{i},\phi^{j}\right] & =0.
\end{align*}
But, at a generic point in the moduli space, these equations won't
have any nontrivial solutions, so the assumption that $\phi^{j}=0$
isn't much of an imposition. 
\end{rem*}
The full moduli space of vacua has a Coulomb branch---identified with
the Hitchin moduli space---and Higgs branches attached to the specific
other points where nontrivial solutions for the $\phi^{j}$ exist.
(Unfortunate nomenclature: the moduli of Higgs bundles is the space
of solutions that live on the Coulomb branch...)


\section{Compactification from (2,0) 6D Theory}

Now let's talk about where that pesky $R$ factor came from. It turns
out that there's a famous 6D $N=\left(2,0\right)$ QFT. It doesn't
have a conventional Lagrangian description (or even a space of fields).
Instead, the inputs are a 6-dimensional manifold, together with a
Lie algebra $\mathfrak{g}$. Call this theory $X_{\mathfrak{g}}$.
It has the following properties:
\begin{itemize}
\item $X_{\mathfrak{g}}$ has $N=\left(2,0\right)$ SUSY in $d=6$. 
\item $X_{\mathfrak{g}}$ has no parameters---no coupling constants or scale,
and the strength of the interaction can't be perturbed.
\item $X_{\mathfrak{g}}$ is conformally invariant. 
\end{itemize}
Despite its unconventional description, we can still compactify $X_{\mathfrak{g}}$
to obtain lower-dimensional theories. In fact, 5D SYM is $X_{\mathfrak{g}}\left[S^{1}\right]$,
where the $R$ is the length of the $S^{1}$. So, $\mathcal{M}_{H}$
is obtained as the moduli space associated to $X_{\mathfrak{g}}\left[C\times S^{1}\right]$.
We could perform this compactification in either order: $\mathcal{M}_{H}$
can also be obtained as the moduli space associated to the theory
$X_{\mathfrak{g}}\left[C\right]$ compactified on $S^{1}$. \cite{GMN}
use this observation to produce canonical Darboux coordinate systems
on $\mathcal{M}_{H}$ and construct Calabi-Yau metrics in these coordinate
systems. 

Some examples of information we can obtain from this perspective:
\begin{itemize}
\item Compactify $X_{\mathfrak{g}}$ on $C$ first to get a 4d $N=2$ supersymmetric
gauge theory with with Coulomb branch $\mathcal{B}$. Then, $\mathcal{B}$
is actually the Hitchin base, i.e., $\mathcal{M}_{H}\rightarrow\mathcal{B}$
with generic fiber a torus. Points $u\in\mathcal{B}$ correspond to
spectral curves $\Sigma_{u}\subset T^{*}C$, also known as ``Seiberg-Witten
curves.''
\item $\mathcal{M}_{H}$ is automatically hyperkahler because of supersymmetry.
\end{itemize}

%% Bibliography
\begin{thebibliography}{AB}
\bibitem[AB]{AB}M.~F.~Atiyah and R.~Bott, The Yang-Mills equations
over Riemann surfaces. Philos.~Trans.~Roy.~Soc. London A 308 (1982)
523--615.

\bibitem[B1]{B1}P.~Boalch, ``Geometry and Braiding of Stokes Data;
Fission and Wild Character Varieties,'' Annals of Math.~\textbf{179}
(2014) 301--365. http://annals.math.princeton.edu/wp-content/uploads/annals-v179-n1-p05-s.pdf 

\bibitem[B2]{B2}P.~Boalch, ``Hyperkaehler Manifolds and Nonabelian
Hodge Theory of (Irregular) Curves,'' arXiv:1203.6607

\bibitem[BB]{BB}O.~Biquard and P.~Boalch. Wild non-abelian Hodge
theory on curves - 2004, Compos.~Math.~140 (2004) 179--204.

\bibitem[BNR]{BNR}A.~Beauville, M.~S.~Narasimhan, and S.~Ramanan,
``Spectral curves and the generalized theta divisor,'' J.~reine
angew.~Math. 398 (1989) 169--179 URL: http://math1.unice.fr/\textasciitilde{}beauvill/pubs/bnr.pdf

\bibitem[D]{D}S.~K.~Donaldson, ``A new proof of a theorem of Narasimhan
and Seshadri,'' J.~Differential Geometry, \textbf{18} (1983) 269--277.

\bibitem[DM]{DM}R.~Donagi and E.~Markman, ``Spectral covers, algebraically
completely integrable Hamiltonian systems, and moduli of bundles.''
arXiv:alg-geom/9507017

\bibitem[FG]{FG}V.~Fock and A.~Goncharov, Moduli spaces of local
systems and higher Teichmueller theory, Publ. Math. Inst. Hautes Etudes
Sci. No. 103 (2006), 1\textendash{}211. 

\bibitem[GMN]{GMN} D.~Giaotto, G.~Moore, and A.~Neitzke, Wall-crossing,
Hitchin systems, and the WKB approximation. arXiv:0907.3987

\bibitem[H1]{H1}N.~Hitchin, ``The self-duality equations on a Riemann
surface,'' Proc. Long. Math. Soc. 55 (1987) 59--126. 

\bibitem[H2]{H2}N.~Hitchin, ``Stable bundles and integrable systems,''
Duke Math J. 54 (1987) 91--114. 

\bibitem[H3]{H3}N.~Hitchin, ``Lie Groups and Teichmueller Space,''
Topology 31 (1992) 449--473. 

\bibitem[HT]{HT}T.~Hausel and M.~Thaddeus. Mirror symmetry, Langlands
duality, and the Hitchin system. Invent. Math., 153 (1):197\textendash{}229,
2003. 

\bibitem[KW]{KW}A.~Kapustin and E.~Witten, ``Electric-Magnetic
Duality and the Geometric Langlands Program,'' CNTP 1 (2007()1--236.
arXiv:hep-th/0604151

\bibitem[N]{N}A.~Neitzke, ``Hitchin systems in N=2 field theory,''
https://www.ma.utexas.edu/users/neitzke/expos/hitchin-systems.pdf 

\bibitem[NS]{NS}M.~S.~Narasimhan and C.~S.~Seshadri, `Stable
and unitary vector bundles on a compact Riemann surface,' Ann.~of
Math.~\textbf{82} (1965) 540--567.

\bibitem[W]{W}E.~Witten, ``Gauge Theory and Wild Ramification,''
arXiv:0710.0631\end{thebibliography}

\end{document}
